
# bbc scores

```{r}
library(tidyverse)
library(rvest)
```

```{r}
url <- "https://www.bbc.com/sport/rugby-league/scores-fixtures"
html <- read_html(url)
```

#betfred-championship-nullround-container > ul > li:nth-child(4) > a > article > div > span.sp-c-fixture__team.sp-c-fixture__team--home > span.sp-c-fixture__team-name.sp-c-fixture__team-name--home > span > span
#betfred-championship-nullround-container > ul > li:nth-child(4) > a > article > div > span.sp-c-fixture__team.sp-c-fixture__team--home > span.sp-c-fixture__team-name.sp-c-fixture__team-name--home > span > abbr





```{r}
html %>% html_elements("article abbr") -> abbrs
abbrs %>% html_attr("title") -> titles
abbrs %>% html_attr("class") -> classes
tibble(classes, titles) %>% 
  filter(str_detect(classes, "sp-c-fixture")) %>% select(team = titles) -> teams
teams
```

#betfred-championship-nullround-container > ul > li:nth-child(3) > a > article > div > span.sp-c-fixture__team.sp-c-fixture__team--home > span.sp-c-fixture__block > span

```{r}
html %>% html_elements("span.sp-c-fixture__block") %>% html_text() -> scores
ng <- nrow(teams) %/% 2
# ng
teams %>% mutate(score = scores) %>% 
  mutate(col = rep(1:2, times = ng),
         row = rep(1:ng, each = 2),
         item = str_c(team, " ", score)) %>% 
  select(item, row, col) %>% 
  pivot_wider(names_from = col, values_from = item) %>% View("scores")
```

